---
title: "GitHub Presentation"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outline

- GitHub: why use it?
- cool features
- new section
- connect with RStudio project
- collaborating on GitHub
- Berry Consultants GitHub Organization

## Using GitHub through RStudio


## Berry Consultants GitHub Organization
- A free option, GitHub Free, with unlimited collaborators on unlimited public repositories with full features and unlimited private repositories with limited features.
- The option to upgrade to GitHub Team or GitHub Enterprise Cloud for additional features, including sophisticated user authentication and management, and escalated support options. For more information, see "GitHub's products."
- Unlimited membership with a variety of roles that grant different levels of access to the organization and its data
- The ability to give members a range of access permissions to your organization's repositories
- Nested teams that reflect your company or group's structure with cascading access permissions and mentions
- The ability for organization owners to view members' two-factor authentication (2FA) status
- The option to require all organization members to use two-factor authentication
- The option to purchase a license for GitHub Advanced Security and use the features on private repositories.

## Slide with Plot

```{r pressure}
plot(pressure)
```

